---
title: "README"
author: "Ntai Lesenya"
date: "October 2020"
output: RMD

PURPOSE:
To Track progress and roadmap of the coding and functions used in the analysis of Us dollar volatility Vs EM and DM equity market performance. 

## Loading Xls data and converting to rds
Finassn1.loc.root <- file.path("C:/Users/User/Documents/finassn1")
Finassn1.loc.subdirs <- c("data", "code", "bin")
Finassn <- build_path(glue::glue("{Finassn1.loc.root}/{Finassn1.loc.subdirs}"))
library(rmsfuns)
load_pkg("readr")
data<- read_csv("C:/Users/User/Documents/Finassn1/data/msci_cleaned.csv")
DataLoc <- Finassn[grepl("data", Finassn)]
write_rds(data, path = file.path(DataLoc, "msci_cleaned.rds"))
rm(data)
data <- read_rds(file.path(DataLoc, "msci_clean.rds"))



## Creating Rmardown and associated packages
if (!require("devtools")) install.packages("devtools")
library(devtools)
devtools::install_github("Nicktz/Texevier")
library(Texevier)
dir <- "C:/Users/User/Documents/finassn1"
create_template(directory = dir, template_name = "Impact of Dollar Volatility on EM & DM eqiuty returns")
install.packages(c('tinytex', 'rmarkdown'))
tinytex::install_tinytex()




Firstly, this function is responsible for loading some core packages needed for the project code:
```{r load packages}
library(rmsfuns)
pacman::p_load("MTS", "robustbase")
pacman::p_load("tidyverse", "devtools", "rugarch","rmgarch", "forecast", "tbl2xts", "lubridate", "PerformanceAnalytics", "Texevier", "ggthemes")

  

```


Then, load the data and subset the sample (pre and post-crisis).

```{r load data }
# -------------------------------------------------------- Load data ------------------------------------------------------
data<- read_rds("C:/Users/User/Documents/finassn1/data/msci_clean.rds")                                                                        

```

DATA
This section details all the needed code used in the data description section of the paper:
The first function below calculates the weekly returns of the msci indices used:
```{r weekly return function}
WeeklyReturnFunction <- function(data){
  
  rtn <- data %>% gather(Tickers, TRI, -Date) %>% group_by(Tickers) %>%
  mutate(dlogret = log(TRI) - log(lag(TRI))) %>% mutate(scaledret = (dlogret -
                                                                       mean(dlogret, na.rm = T))) %>% filter(Date > first(Date)) %>%
  ungroup()
Tidyrtn <- rtn


  g <-
ggplot(Tidyrtn) + geom_line(aes(x = Date, y = TRI, colour = Tickers,
                                alpha = 0.5)) + ggtitle("MSCI Returns Series:  EM  & DM Returns") +
  facet_wrap(~Tickers, scales = "free_y") + guides(alpha = FALSE) +
  theme_bw() + scale_color_hue(l = 20) + scale_x_date(labels = scales::date_format("'%y"),
                                                      date_breaks = "2 years") + theme(axis.text = element_text(size = 7)) # However the plot will be inserted in the Appedix in the actual paper for cleanliness

}

```
#Test for Heteroskedasticity in the data using the MV contitional Heteroskedasticity test. This confirms the financial time series characteristic of non-nomarlity and use of GARCH modelling
xts_rtn <- rtn %>% tbl_xts(., cols_to_xts = "dlogret", spread_by = "Tickers")
MarchTest(xts_rtn)

This code design a table for Ticker description (However the table will be inserted in the Appedix in the actual paper for cleanliness):

library(xtable)
des_names <- c("Brazil", "Canada", "Switzerland", "France", "United Kingdom", "India", "Japan", "South Africa", "Taiwan","Egypt", "Bloomberg US Dollar Spot Index")

des_t <- cbind(colnames(xts_rtn), des_names)
colnames(des_t) <- c("Ticker", "Description")

table <- xtable(des_t, caption = "Returns description Table \\label{tab1}")
print.xtable(table,
             # tabular.environment = "longtable",
             floating = TRUE,
             table.placement = 'H',
             # scalebox = 0.4,
             comment = FALSE,
             caption.placement = 'bottom'
)

Use this code to design a summary statistics for the time series data and filter out less important stats: 
# Descriptive stats table

pacman::p_load("psych")
rtn_tbl<-rtn
rtn_tbl$Date <- NULL
rtn_tbl$scaledret <- NULL
rtn_tbl$TRI <-NULL
des_table <- psych::describeBy(rtn_tbl, rtn_tbl$Tickers, mat = TRUE)
des_table$item <- NULL
des_table$range <- NULL
des_table$mad <- NULL
des_table$n <- NULL
des_table$Date<-NULL
des_table$vars<-NULL
des_table <- des_table[ -(1:11), ]
table <- xtable(des_table, caption = "Descriptive Statistics Table \\label{tab2}")
print.xtable(table,
             tabular.environment = "longtable",
             floating = TRUE,
             table.placement = 'H',
             scalebox = 0,
             comment = FALSE,
             caption.placement = 'bottom'
)




METHODOLOGY
Following the test then we can settle on the DCC GARCH model. This section breaks down the derivations of the dynamic conditional correlations:




RESULTS
This section details all the needed code used to obatin the results analysed in the PAPER:
## DCC-GARCH
Apply the following code chunk to calculate the individual volatility series to be used in DCC estimation:
    
```{r VOL_series}

#Firstly for the individual series, a standard univariate GARCH(1,1) modelled to give the H_t (used interchangeably with Sigma for plotting) process to be used in calculating the standardized residual. This are then used in  DCC calculations after.

DCCPre <- dccPre(xts_rtn, include.mean = T, p = 0) #dccPre fits the univariate GARCH models to each series of returns
names(DCCPre)

Vol_series <- DCCPre$marVol
colnames(Vol_series) <- colnames(xts_rtn)
library(dplyr)
Vol_series <-
  data.frame( cbind( date = index(xts_rtn), Vol_series)) %>% # Add date column which dropped away...
  mutate(date = as.Date(date)) %>%  tbl_df()  # make date column a date column...
TidyVol <- Vol_series %>% gather(Tickers, Sigma, -date)
g2 <-
ggplot(TidyVol) + geom_line(aes(x = date, y = Sigma, colour = Tickers)) # However the plot will be inserted in the Appedix in the actual paper for cleanliness

```

The following code chunk uses the standaedised residuals to estimate the time-varying conditional correlations between USD and EM-DM equity returns:

```{r DCC model estimation}
#==============================================================================
### Estimating DCC model
#=============================================================================

#WE firstly save the standardized residuals (Etas) from the Vol series above

StdRes <- DCCPre$sresi

#detach tidyr and dplyr packages to avoid ambiguity between stats::filter and dplyr::filter
detach("package:tidyverse", unload=TRUE)
detach("package:tbl2xts", unload=TRUE)

#run the dccFit to calculate DCC using the starndadised residuals

DCC <- dccFit(StdRes, type="Engle")

#reload packages

pacman::p_load("tidyverse", "tbl2xts", "broom")

##calculating bivariate correlation between pairs

#plot all the bivariate time-varying correlations with BBDXY
Rhot <- DCC$rho.t

#Loop to clean plot by create a renaming function(katzke 2020)
ReturnSeries = xts_rtn
DCC.TV.Cor = Rhot

#To clean the plot 
renamingdcc <- function(ReturnSeries, DCC.TV.Cor) {
  
  ncolrtn <- ncol(ReturnSeries)
  namesrtn <- colnames(ReturnSeries)
  paste(namesrtn, collapse = "_")
  
  nam <- c()
  xx <- mapply(rep, times = ncolrtn:1, x = namesrtn)
  # Now we create a nested for loop to save the names corresponding to the columns of interest.. 
  
   nam <- c()
  for (j in 1:(ncolrtn)) {
    for (i in 1:(ncolrtn)) {
      nam[(i + (j-1)*(ncolrtn))] <- paste(xx[[j]][1], xx[[i]][1], sep="_")
    }
  }
  
  colnames(DCC.TV.Cor) <- nam
  
  # So to plot all the time-varying correlations wrt BBDXY
      
  # First append the date column that has (again) been removed...
  
  DCC.TV.Cor <- 
    data.frame( cbind( date = index(ReturnSeries), DCC.TV.Cor)) %>% # Add date column which dropped away...
    mutate(date = as.Date(date)) %>%  tbl_df() 
  
  DCC.TV.Cor <- DCC.TV.Cor %>% gather(Pairs, Rho, -date)
  
  DCC.TV.Cor
  
}

#Now run the function
Rhot <- 
  renamingdcc(ReturnSeries = xts_rtn, DCC.TV.Cor = Rhot)

head(Rhot %>% arrange(date))


  ## create a plot for all the stocks relative to the other stocks
  
g1 <- 
    ggplot(Rhot %>% filter(grepl("MXBR_", Pairs ), !grepl("_MXBR", Pairs)) ) + 
    geom_line(aes(x = date, y = Rho, colour = Pairs)) + 
    theme_hc() +
    ggtitle("Dynamic Conditional Correlations: MXBR")
  
print(g1)
## However the paper only captures code and subsequent plot for the BBDXY relative to all the stocks as set out in the objective
g2 <- 
    g1 %+% subset(Rhot %>% filter(grepl("BBDXY_", Pairs ), !grepl("_BBDXY", Pairs))) + ggtitle("Dynamic Conditional Correlations: BBDXY") #(However the plot will be inserted in the Appedix in the actual paper for cleanliness)
 
print(g2)
```

